
## **1. What are Internal Hyperlinks?**

Internal hyperlinks are links that **jump to a specific section within the same webpage**.

Example:
Click "Hyderabad" → Page scrolls to the Hyderabad section.

---

## **2. How Internal Links Work**

Internal links use two things:

### **(1) `id` Attribute**

Used to **mark a location** on the page.

Example:

```html
<h2 id="Hyd">Hyderabad</h2>
```

### **(2) `<a href="#idName">`**

Used to **jump to that location**.

Example:

```html
<a href="#Hyd">Hyderabad</a>
```

➡️ `#Hyd` tells the browser to scroll to the element with `id="Hyd"`.

---

## **3. Why Use Internal Hyperlinks?**

They are useful in:

✔ Long pages
✔ Table of contents
✔ Navigation menus
✔ Jump-to-top buttons

---

## **4. Explanation of Your Code**

### **Title & Favicon**

```html
<title>facebook - login page</title>
<link rel="icon" href="image.png"/>
```

* The title appears on the browser tab
* The favicon shows a small icon (image.png file)

---

## **Top Heading**

```html
<h2 id="top">demo on internal hyperlinks</h2>
```

* `id="top"` lets us jump back to the top from any section.

---

## **Navigation Links**

```html
<p align="center">
    <a href="#Hyd">Hyderabad</a>
    <a href="#Niz">Nizamabad</a>
    <a href="#Ktg">Kotagiri</a>
</p>
```

* These links allow the user to jump to specific city sections.
* `align="center"` centers the links.

---

## **Destination Sections**

### **Hyderabad Section**

```html
<h2 id="Hyd"><u>Hyderabad</u></h2>
Bn Reddy <br>
<a href="#top">top</a>
```

* `id="Hyd"` is the target for the Hyderabad link.
* `<a href="#top">top</a>` takes the user back to the top.

---

### **Nizamabad Section**

```html
<h2 id="Niz"><u>Nizamabad</u></h2>
Nagaram <br>
<a href="#top">top</a>
```

---

### **Kotagiri Section**

```html
<h2 id="Ktg"><u>Kotagiri</u></h2>
temple <br>
<a href="#top">top</a>
```

---

## ⭐ **Important Points**

* IDs must be **unique**.
* **Case-sensitive** → `Ktg` ≠ `ktg`.
* `#` symbol is required in internal links.
* Internal links work **only within the same page**.
* Use `id` to mark the destination.
* Use `<a href="#id">` to jump to the destination.

---

## 🎯 **Extra Tip**

Always keep your section IDs simple and meaningful:

* `#top`
* `#about`
* `#contact`
* `#services`

